Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-07 paper/ms.tex
Incorporate JH suggestions (part 2)
Co-authored-by: Joel Hartman <jhartman@astro.princeton.edu>

\edit1{Carl TODO: please describe and correct as appropriate}
The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.  Star B was not detected; with a separation of $5.4''$ from
\tn, it fell outside the field of view.

@@

>>>>

The observations of \tn\ were initially acquired by
\citet{ziegler_soar_2020} as part of the Southern Astrophysical
Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
show the resulting measured 5-$\sigma$ detectable contrasts.  The
lines are linear smoothing fits between the regimes of the diffraction
limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
$\approx 1.5''$, beyond which the speckle patterns become
de-correlated.  Star A (TIC 847769574) was detected at the expected
location and brightness contrast, and no additional companions were
found.  Star B was not detected; with a separation of $5.4''$ from
\tn, it fell outside the field of view.

@@

One potential caveat in our approach is that \texttt{VESPA} uses a galactic
population synthesis to model the sight-line. Since \tn\ is in the
foreground of \cn\ (see Section~\ref{subsec:star}), for roughly
$25\,{\rm pc}$ behind the sightline to the star, the number of
background stars is higher than \texttt{VESPA} would predict due to the
presence of the cluster.  To quantify the importance of this effect,
we assessed the sky-plane density of potential contaminants by
counting stars brighter than $T=15.07$ within 0.5 degrees of \tn\
\citep{stassun_TIC8_2019}. We then compared this density against
sightlines rotated in galactic longitude towards and away from the
galactic center. Within $\pm10^\circ$ in galactic longitude, the
sky-plane density of stars fluctuated at the level of $\approx 15\%$,
with a local maximum a few degrees away from \tn, towards the center of \cn.
The overall density also slowly increased towards the galactic center.
We therefore do not expect this consideration to significantly alter
our FPP calculation.
